Reanalysis Step 1: Data Preparation

### 2025-08-26 reanalysis-1-data_preparation.qmd
bugfix

# Complete cases should have no missing data in key analysis variables
# This includes outcome, exposure, and all covariates
key_vars_for_complete <- c(
  "outcome_VA_logMAR",  # Outcome
  "ever_lapse_binary",   # Exposure
  "baseline_VA_logMAR",  # Key covariate
  "CCI", "DCSI",        # Comorbidity scores
  "dr_severity",         # DR severity
  "any_treatment"        # Treatment status
)

df_complete_original <- df_analysis |>
  filter(complete.cases(select(., all_of(key_vars_for_complete))))

>>>>

# Complete cases should have no missing data in key analysis variables
# This includes outcome, exposure, and all covariates
key_vars_for_complete <- c(
  "outcome_VA_logMAR",  # Outcome
  "ever_lapse_binary",   # Exposure
  "baseline_VA_logMAR",  # Key covariate
  "CCI", "DCSI",        # Comorbidity scores
  "any_treatment"        # Treatment status
)

df_complete_original <- df_analysis |>
  filter(complete.cases(pick(all_of(key_vars_for_complete))))
